Abstraction and Invariance for Algebraically Indexed Types

### 2012-10-29 paper/section-introduction.tex
Fix font of 'areaTri' in introduction

\paragraph{Invariance}
To illustrate type-induced invariance properties, consider
two-dimensional geometry. 
In a conventional type system, a function $\mathit{areaTri}$ that computes the area of a triangle
might be assigned the type:
$\tyPrimNm{vec}\times\tyPrimNm{vec}\times\tyPrimNm{vec}\tyArr\tyReal$.
But in our proposed system we can assign it the following more expressive polymorphic
type:
\[
\mathrm{areaTri} : \forall t\mathord:\SynTransl{2}.
  \tyPrim{vec}{t} \times \tyPrim{vec}{t} \times \tyPrim{vec}{t} \to \tyReal \\
\]
This type expresses the fact that if each of the arguments to $\mathrm{areaTri}$
is translated by the same vector, then the result remains the same,
that is, it is \emph{invariant} under translation. Formally, for any 
vector $\vec t$,
\[
\mathrm{areaTri}\;(\vec{t} + \vec{v_1}, \vec{t} + \vec{v_2}, \vec{t} + \vec{v_3}) = 
\mathrm{areaTri}\;(\vec{v_1}, \vec{v_2}, \vec{v_3})
\]

>>>>

\paragraph{Invariance}
To illustrate type-induced invariance properties, consider
two-dimensional geometry. 
In a conventional type system, a function $\mathrm{areaTri}$ that computes the area of a triangle
might be assigned the type:
$\tyPrimNm{vec}\times\tyPrimNm{vec}\times\tyPrimNm{vec}\tyArr\tyReal$.
But in our proposed system we can assign it the following more expressive polymorphic
type:
\[
\mathrm{areaTri} : \forall t\mathord:\SynTransl{2}.
  \tyPrim{vec}{t} \times \tyPrim{vec}{t} \times \tyPrim{vec}{t} \to \tyReal \\
\]
This type expresses the fact that if each of the arguments to $\mathrm{areaTri}$
is translated by the same vector, then the result remains the same,
that is, it is \emph{invariant} under translation. Formally, for any 
vector $\vec t$,
\[
\mathrm{areaTri}\;(\vec{t} + \vec{v_1}, \vec{t} + \vec{v_2}, \vec{t} + \vec{v_3}) = 
\mathrm{areaTri}\;(\vec{v_1}, \vec{v_2}, \vec{v_3})
\]
